Designing Turk Experiments for Visual Statistical Inference

### 2013-07-23 paper_turk.tex
finished review

\item It is recommended to reject the task if it is not submitted as requirement. Some times this may produce dispute and the workers may become angry and demand payment. We recommend to be strict to the decision and for any further administrative control there is an option to block the worker if necessary. After all this is a work place and it is expected that the worker maintain the work place environment.

@@

We have performed 10 different experiments using the web application described in Section~\ref{sec:web_application}. Table~\ref{tbl:mturk} presents the tasks and payment details of all the 10 experiments. Experiment 1 was the first experiment and the largest number of tasks were rejected in that experiment. But this experiment provides valuable information about how to modify the web site to avoid invalid input and missing information. Thus in the later experiments we did not see a lot of tasks to get rejected.

@@

The hourly payment rates shown in Table~\ref{tbl:mturk} are based on the time periods beginning from the times the tasks were accepted by the worker to the time they were submitted to the MTurk system. It is different from the time taken to actually evaluate the lineups. Since in between the workers need to go to the web application, get the codes after they finish the tasks and finally put the code to MTurk system. The pay rate is almost similar for all the experiment except for experiment 2. The payment was decided based on the MTurk standard of \$6 per hour and we can see that for experiment 2. Based on the experiment 1 and 2, they payment for each task was fixed to \$1, but in practice, it appears to be much less than that. It is because, workers spent long time in between lineups.

@@

Figure~\ref{fig:task_duration} shows the comparative durations of time for 100 tasks in each of the experiment. Even though experiment 8 (sine illusion) took longer to finish it got the least number of rejected tasks.

@@

\section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated. The online application design provides features to control how the multiple lineups can be presented to an observer. Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot. This also made the multiple plot selection from a lineup easier and convenient. The web site is used for multiple online experiments.

@@

The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their need and run the MTurk experiments as part of their research that involves lineups. This will also help lineup protocol to be used frequently since it will provide an ease of its use in making inferential decisions.

>>>>

\item It is recommended to reject the task if it is not submitted as required. Some times this may produce dispute and the workers may become upset and still demand payment. We recommend to be strict to the decision and for any further administrative control there is an option to block the worker if necessary. After all this is a work place and it is expected that the worker maintain the work place environment.

@@

We have performed 10 different experiments using the web application described in Section~\ref{sec:web_application}. Table~\ref{tbl:mturk} presents the tasks and payment details of all the 10 experiments. Experiment 1 was the first experiment and the largest number of tasks were rejected in that experiment. But this experiment provides valuable information about how to upgrade the web site to avoid invalid input and missing information. Thus in the later experiments we did not see a lot of tasks to get rejected.

@@

The hourly payment rates shown in Table~\ref{tbl:mturk} are based on the time periods beginning from the times the tasks were accepted by the worker to the time they were submitted to the MTurk system. It is different from the time taken to actually evaluate the lineups. Since in between the workers need to go to the web application, get the codes after they finish the tasks and finally put the code to MTurk system. The pay rate is almost similar for all the experiment except for experiment 2. The payment amount was decided based on the MTurk standard of \$6 per hour and we can see that for experiment 2. Based on the experiment 1 and 2, the payment for each task was fixed to \$1, but in practice, it appears to be much less than that. It is because, workers spent long time in between lineups.

@@

Figure~\ref{fig:task_duration} shows the comparative durations of time for 100 tasks in each of the experiments. Even though experiment 8 (sine illusion) took longer to finish it got the least number of rejected tasks.

@@

\section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated. The online application design provides features to control how the multiple lineups can be presented to an observer. Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot. This also made the multiple plot selections from a lineup easier and convenient. The web site is used for multiple online experiments.

@@

The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their needs and run the MTurk experiments as part of their research that involves lineups. This will also help lineup protocol to be used frequently in making inferential decisions since it will provide the required flexibilities and convenience.
